visualizemi: Visualization, Effect Size, and Replication of Measurement Invariance for Registered Reports

### 2024-07-29 manuscript.Rmd
sigh word docs

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
appendix          :
  - "appendix_1.Rmd"
  - "appendix_2.Rmd"
  - "appendix_3.Rmd"
  - "appendix_4.Rmd"
  - "appendix_5.Rmd"
  - "appendix_6.Rmd"
  - "appendix_7.Rmd"
---

@@

ggsave("figures/rs7-visual.png", dpi = 300, 
       width = 8, 
       height = 6,
       units = "in")
```

@@

ggsave("figures/rs6-visual.png", dpi = 300, 
       width = 8, 
       height = 6, 
       units = "in")
```

>>>>

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_docx
appendix          :
  - "appendix_1.Rmd"
  - "appendix_2.Rmd"
  - "appendix_3.Rmd"
  - "appendix_4.Rmd"
  - "appendix_5.Rmd"
  - "appendix_6.Rmd"
  - "appendix_7.Rmd"
---

@@

ggsave("figures/rs7-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```

@@

ggsave("figures/rs6-visual.png", dpi = 300, 
       width = 8, 
       units = "in")
```
